Topological Equivariant Artist Model for Visualization Library Architecture

### 2024-12-23 paper/main.tex
reworked rho figure + clean ups to text

\begin{figure}
  \includegraphics*[width=1\columnwidth]{tex/equivariant.png}
  \caption{Encoding data as the bar height using an exponential transform is not equivariant because encoding the data and then scaling the bar heights yields a much taller graph then scaling the data and then encoding those heights using the same exponential transform function.}
  \label{fig:related-work:equivariance}
\end{figure}

@@

Although the Steven's scales were conceptualized as having group structure, the ordinal scale has a monoidal structure because partial orders ($\geq, \leq$) are not invertible. This means \textit{equivariance} cannot be used to test for structure preservation. Instead \textit{homomorphism} can be used because it imposes fewer constraints on the underlying mathematical structure of the data.
\begin{figure}
  \includegraphics[width=1\columnwidth]{tex/homomorphism.png}
  \caption{Encoding data as bar height using an inverse transform is not homomorphic because the largest number is mapped to the smallest bar while the max function returns the largest bar.}
  \label{fig:related-work:homomorphism}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{k_different_types.png}
  \caption{This weather station data has multiple embedded continuities - points at each time and position, timeseries at each position, and maps at each time. The corresponding visualizations - bar chart, timeseries, and map - each preserve the continuity of the subset of the data they visualize by not introducing or leaving out values and preserving the relative positioning of continuous values.}
%
  \label{fig:related-work:continuity:ktypes}
\end{figure}

@@

Domain specific libraries are designed with the assumption of continuities that are common in the domain \cite{HeerSoftware2006}, and therefore can somewhat restrict their API to choices that are appropriate for the domain. For example, a tabular topological structure of discrete rows, as illustrated in \autoref{fig:related-work:continuity:ktypes}, is assumed by A Presentation Tool\cite{mackinlayAutomatingDesignGraphical1986, mackinlayAutomatingDesignGraphical1986} and grammar of graphics\cite{wilkinsonGrammarGraphics2005} and the ggplot\cite{wickhamGgplot2ElegantGraphics2016}, vega\cite{satyanarayanDeclarativeInteractionDesign2014}, and altair\cite{vanderplasAltairInteractiveStatistical2018} libraries built on these frameworks. Image libraries such as Napari\cite{nicholas_sofroniew_2021_4533308} and ImageJ\cite{schneiderNIHImageImageJ2012} and its humanities ImagePlot\cite{studiesCulturevisImageplot2021} plugin assume that the input is 2D continuous. Networking libraries such as gephi\cite{bastianGephiOpenSource2009} and networkx\cite{HagbergExploringNetwork2008} assume a graph-like structure. By assuming the structure of their data, these domain specific libraries can provide more cohesive interfaces for a much more limited set of visualization algorithms than the building block libraries offer.

@@

\begin{figure}[!h]
       \includegraphics[width=1\columnwidth]{fb.png}
       \caption{The space of all data values encoded by this fiber bundle can be modeled as a \textcolor{total}{rectangle} total space. Each dataset in this data space lies along the interval \textcolor{base}{$[0,2\pi]$} base space. Each dataset has values along the \textcolor{fiber}{$-1 \rightarrow 1$} interval fiber. One dataset embedded in this total space is the \textcolor{section}{sin} section over the bundle.}\label{fig:atct:fb}
  \end{figure}

@@

\paragraph{Joining indexing spaces: $\oplus: \mathcal{\dbasec} \sqcup \mathcal{\dbasec} \rightarrow \mathcal{\dbasec}$}
For example, the disjoint union of two bundles, as shown in \autoref{fig:atct:local_trivalizations}, is the coproduct $\dbase_{a} \sqcup_{\dbase_{c}} \dbase_{b}$ over an overlap $\dbase_{c}$ and therefore the inclusion morphism must be commutative:
\begin{figure}[h]
  \includegraphics*[width=1\columnwidth]{figures/tex/k_coproduct.pdf}  \caption{Index spaces are combined via the \textit{coproduct} $\dbase_{a}\sqcup_{\dbase_c} \dbase_{b}$.}
  \label{fig:atct:base}
\end{figure}

This means that index spaces are combined on overlapping indices. For example, in \autoref{fig:atct:base}, the open interval $\dbase_c$ is present in both $\dbase_a$ and $\dbase_c$; therefore $\dbase_a$ and $\dbase_b$ are glued together where they overlap at $\dbase_c$.  Two spaces have been combined correctly if every point in the overlap  $\dbasepoint \in \dbase^{c}$ is present in each of the spaces $\dbasepoint \in \dbase^{a}$ and $\dbasepoint \in \dbase^{b}$ such that it is present in the joined space $\dbasepoint \in \dbase^{a}\sqcup_{\dbase^{c}} \dbase_{b}$. This simple test that the records are joined correctly is what allows us to reliably build larger datasets out of smaller ones, such as in the case of distributed and on demand datasets.

@@

Combining fibers correctly can be verified by checking that when a fiber component $\dfiber^{c}$ is present in both $\dfiber^{a}$ and $\dfiber^{b}$, it is identical when projected out of either such that the \textit{product} diagram commutes:

@@

This means that when data with many fields is decomposed into its component fields, records maintain their integrity. For example in \autoref{fig:atct:fiber} the red (temperature, time, pressure) record separates into (temperature, time) and (pressure, time) records that share the same red time. Furthermore this time is the same whether it is obtained from the (temperature, time) or (pressure, time) record. Generally, the test for joining fields is that when a record is present in a fiber $\delement_{c} \in \pi_c(\dfiber_{a}), \delement_c \in \pi_c(\dfiber_{b})$ then it is in the joint record $\delement_{c} \in \pi_c(\dfiber_{a}\times_{\dfiber_c}\dfiber_{b})$ when is in the field $\dfiber_c$ being joined on. This simple test that fields are joined together correctly for the same record is what allows us to reliably combine multiple datasets together on shared properties, for example growing the weather station data in \autoref{fig:related-work:continuity:ktypes} from a temporal to spatial dataset by adding the weather at each location at each time.

\subsubsection{\textcolor{section}{Data: Section}}
\label{sec:atct:fb:sections}
We encode data as a \textcolor{section}{section} \dsectionc\ of a bundle because this allows us to incorporate the topology and field types in the data definition. We define section functions locally, meaning that the section is (piece-wise) continuous over a specific open subset \openset\ of \dbase\:
\begin{equation}
  \label{eq:atct:fb:sections}
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}
\end{equation}
such that each section function $\dsection: \dbasepoint \mapsto \delement$ maps from each point $\dbasepoint \in \openset$ to a corresponding record in the fiber space $\delement \in \dfiber_{\dbasepoint}$ over that point. Bundles can have multiple sections, as denoted by $\Gamma(\openset, \dtotal\restriction{\openset})$. We can therefore model data as structures that map from an index like point $\dbasepoint$ to a data record $\delement$, and encapsulate multiple datasets with the same fiber and base space as different sections of the same bundle.

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{fb_rho.png}
  \caption{The scatter marker is specified by the section $\gsection$, which maps into the fiber $\gfiber$ to retrieve the values that compose into the pixel (approximated as a square) returned by the section function evaluated at each point $\gbasepoint$. The section evaluated over the entire space $\gsection\vert_{S}$ returns the entire scatter mark, shown here in faded form to make it easier to see the individual pixels.
  \label{fig:atct:fb:graphic}}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[width=1\columnwidth]{tex/sheaf_rules.png}
  \caption{A sheaf has the conditions that sections are equal when they match on all subsets (\textit{locality}) and that the sections can be concatenated when they match on overlaps \textit{gluing}.\label{fig:atct:sheaf}}
\end{figure}

@@

\subsubsection{Example: Graphic and Data}
\begin{figure}[H]
  \includegraphics*[width=1\columnwidth]{xi_diagram.png}
  \caption{The data consists of the $sin$ and $cos$ functions over a unit circle base space. We choose to visualize this as a circle and two line plots. The indexing function \vindex\ book keeps \note{find better word than bookkeeping} which parts of the circle and each curve correspond to each point on the unit circle. The pushforward $\vindexpush$ matches each point in the data space to the specification of the graphic at that point, while the pullback $\vindexpull$ matches each point in the graphic space to the data over that point. \label{fig:atct:morphisms:sheaf}}
\end{figure}

@@

\begin{table}[H]
  \centering
  {\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|r | l l | }
    \hline
     & \textcolor{section}{section} & \textcolor{sheaf}{sheaf} \\
     & record at location & set of possible records for subset \\
     \hline
  Data & $ \cgamma{\dbasec}{\dtotalc} \ni \dsectionc: \dbase \textcolor{section}{\rightarrow} \dfiberc$ & $\sheafc_{\dbasec, \dtotalc}: \opensetc \rightarrow \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$\\
  Visual &  $\cgamma{\dbasec}{\vtotalc} \ni \vsectionc: \dbase \textcolor{section}{\rightarrow} \vfiberc$ & $\sheafc_{\dbasec, \vtotalc}: \opensetc \rightarrow \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}$\\
  Graphic &    $\cgamma{\gbasec}{\gtotalc} \ni \gsectionc: \gbase \textcolor{section}{\rightarrow} \gfiberc$ &  $\sheafc_{\gbasec, \gtotalc}: \opensetgc \rightarrow \cgamma{\opensetc}{\gtotalc\restriction_{\opensetgc}}$ \\
  \hline
  \end{tabular}
  \caption{Functions that associate topological subspaces with records, discussed in \autoref{sec:atct:fb:sections} and \autoref{sec:atct:sheaves}}
  \label{tab:appendix:summary:datafunctions}
  }
\end{table}
\begin{table}[H]
  \centering
  {\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|r|l|}
    \hline
      axiom & applied to datasets and indexes \\
    \hline
     presheaf & given $\textcolor{base}{index_1} \subset \textcolor{base}{index_2}$:\\
        & $\exists\;\textcolor{section}{dataset}[\textcolor{base}{index_2}]$\\
      & $\Rightarrow \textcolor{section}{dataset}[\textcolor{base}{index_2}][\textcolor{base}{index_1}] = \textcolor{section}{dataset}[\textcolor{base}{index_1}]$\\
     &  $\exists\;\textcolor{section}{dataset}[\textcolor{base}{index_1}] \nRightarrow \exists\;\textcolor{section}{dataset}[\textcolor{base}{index_2}]$\\
     &\\
    \hline
    locality & $\textcolor{section}{dataset^1}[\textcolor{base}{i}] = \textcolor{section}{dataset^2}[\textcolor{base}{i}]\;\forall\; \textcolor{base}{i}\in \textcolor{base}{index}\;$ \\
     & $\Rightarrow \textcolor{section}{dataset^1}=\textcolor{section}{dataset^2}$ \\
    \hline
    gluing & $\textcolor{base}{i}=\textcolor{base}{j}$ and $\textcolor{section}{dataset^1}[\textcolor{base}{i}] = \textcolor{section}{dataset^2}[\textcolor{base}{j}]$ \\
     & $\textcolor{section}{dataset^3}\coloneq  \textcolor{section}{dataset^1}[\textcolor{base}{:i}]  \oplus \textcolor{section}{dataset^2}[\textcolor{base}{j:}]$ \\
\hline
  \end{tabular}
  \caption{Presheaf and sheaf constraints implemented by structure preserving data containers, discussed in \autoref{sec:atct:sheaves}}
  \label{tab:appendix:summary:sheaves}
  }
\end{table}

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{transition_maps.png}
  \caption{The cylinder is a trivial fiber bundle; therefore it can be decomposed into local trivalizations that only need identity
  maps to glue the trivializations together. The mobius band is a non-trivial bundle; therefore it can only be decomposed into trivializations where at least one transition map is not an identity map. }\label{fig:cyl_mob_bundles}
\end{figure}

@@

\section*{Acknowledgment}
\note{Acknowledge all the actual people}
The authors would like to thank the anonymous reviewers who gave constructive feedback on
an earlier version of this paper. Various Matplotlib and Napari contributors, particularly
Juan Nunez-Iglesias , and Nicolas Kruchten have provided valuable feedback from the
library developers perspective.

>>>>

\begin{figure}
  \includegraphics*[width=1\columnwidth]{equivariant.pdf}
  \caption{Encoding data as the bar height using an exponential transform is not equivariant because encoding the data and then scaling the bar heights yields a much taller graph then scaling the data and then encoding those heights using the same exponential transform function.}
  \label{fig:related-work:equivariance}
\end{figure}

@@

Although the Steven's scales were conceptualized as having group structure, the ordinal scale has a monoidal structure because partial orders ($\geq, \leq$) are not invertible. This means \textit{equivariance} cannot be used to test for structure preservation. Instead \textit{homomorphism} can be used because it imposes fewer constraints on the underlying mathematical structure of the data.
\begin{figure}
  \includegraphics[width=1\columnwidth]{homomorphism.pdf}
  \caption{Encoding data as bar height using an inverse transform is not homomorphic because the largest number is mapped to the smallest bar while the max function returns the largest bar.}
  \label{fig:related-work:homomorphism}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{k_different_types.pdf}
  \caption{This weather station data has multiple embedded continuities - points at each time and position, timeseries at each position, and maps at each time. The corresponding visualizations - bar chart, timeseries, and map - each preserve the continuity of the subset of the data they visualize by not introducing or leaving out values and preserving the relative positioning of continuous values.}
%
  \label{fig:related-work:continuity:ktypes}
\end{figure}

@@

Domain specific libraries are designed with the assumption of continuities that are common in the domain \cite{HeerSoftware2006}, and therefore can somewhat restrict their API to choices that are appropriate for that domain. For example, a tabular topological structure of discrete rows, as illustrated in \autoref{fig:related-work:continuity:ktypes}, is assumed by A Presentation Tool\cite{mackinlayAutomatingDesignGraphical1986, mackinlayAutomatingDesignGraphical1986} and grammar of graphics\cite{wilkinsonGrammarGraphics2005} and the ggplot\cite{wickhamGgplot2ElegantGraphics2016}, vega\cite{satyanarayanDeclarativeInteractionDesign2014}, and altair\cite{vanderplasAltairInteractiveStatistical2018} libraries built on these frameworks. Image libraries such as Napari\cite{nicholas_sofroniew_2021_4533308} and ImageJ\cite{schneiderNIHImageImageJ2012} and the ImagePlot\cite{studiesCulturevisImageplot2021} art plugin assume that the input is a 2D continuous image. Networking libraries such as gephi\cite{bastianGephiOpenSource2009} and networkx\cite{HagbergExploringNetwork2008} assume a graph-like structure. By assuming the structure of their data, these domain specific libraries can provide more cohesive interfaces because a limited set of visualization algorithms apply to their data and the visualizations these algorithms provide can be styled in a fixed number of ways.

@@

\begin{figure}[!h]
       \includegraphics[width=1\columnwidth]{fb.pdf}
       \caption{The space of all data values encoded by this fiber bundle can be modeled as a \textcolor{total}{rectangle} total space. Each dataset in this data space lies along the interval \textcolor{base}{$[0,2\pi]$} base space. Each dataset has values along the \textcolor{fiber}{$-1 \rightarrow 1$} interval fiber. One dataset embedded in this total space is the \textcolor{section}{sin} section over the bundle.}\label{fig:atct:fb}
  \end{figure}

@@

\paragraph{Joining indexing spaces: $\oplus: \mathcal{\dbasec} \sqcup \mathcal{\dbasec} \rightarrow \mathcal{\dbasec}$}
Joining two bundles on their base space, for example to glue the two trivializations in \autoref{fig:atct:fb} into a bundle, is the coproduct $\dbase_{a} \sqcup_{\dbase_{c}} \dbase_{b}$ over a space $\dbase_{c}$. A property of the coproduct is that the inclusion morphism must be commutative, which means that index spaces are combined on overlapping indices:
\begin{figure}[h]
  \includegraphics*[width=1\columnwidth]{figures/tex/k_coproduct.pdf}  \caption{Index spaces are combined via the \textit{coproduct} $\dbase_{a}\sqcup_{\dbase_c} \dbase_{b}$.}
  \label{fig:atct:base}
\end{figure}
 For example, in \autoref{fig:atct:base}, the open interval $\dbase_c$ is present in both $\dbase_a$ and $\dbase_c$; therefore $\dbase_a$ and $\dbase_b$ are glued together where they overlap at $\dbase_c$.  Two spaces have been combined correctly if every point in the overlap  $\dbasepoint \in \dbase^{c}$ is present in each of the spaces $\dbasepoint \in \dbase^{a}$ and $\dbasepoint \in \dbase^{b}$ such that it is present in the joined space $\dbasepoint \in \dbase^{a}\sqcup_{\dbase^{c}} \dbase_{b}$. This simple test that the records are joined correctly is what allows us to reliably build larger datasets out of smaller ones, such as in the case of distributed and on demand datasets.

@@

Combining fibers correctly can be verified by checking that when a fiber component $\dfiber^{c}$ is present in both $\dfiber^{a}$ and $\dfiber^{b}$, it is identical when projected out of either such that the \textit{product} diagram commutes, means that when data with many fields is decomposed into its component fields, records maintain their integrity:

@@

For example in \autoref{fig:atct:fiber} the red (temperature, time, pressure) record separates into (temperature, time) and (pressure, time) records that share the same red time. Furthermore this time is the same whether it is obtained from the (temperature, time) or (pressure, time) record. Generally, the test for joining fields is that when a record is present in a fiber $\delement_{c} \in \pi_c(\dfiber_{a}), \delement_c \in \pi_c(\dfiber_{b})$ then it is in the joint record $\delement_{c} \in \pi_c(\dfiber_{a}\times_{\dfiber_c}\dfiber_{b})$ when is in the field $\dfiber_c$ being joined on. This simple test that fields are joined together correctly for the same record is what allows us to reliably combine multiple datasets together on shared properties, for example growing the weather station data in \autoref{fig:related-work:continuity:ktypes} from a temporal to spatial dataset by adding the weather at each location at each time.

\subsubsection{\textcolor{section}{Data: Section $\dsection$}}
\label{sec:atct:fb:sections}
We encode data as a \textcolor{section}{section} \dsectionc\ of a bundle because this allows us to incorporate the topology and field types in the data definition. We define section functions locally, meaning that the section is (piece-wise) continuous over a specific open subset \openset\ of \dbase\:
\begin{equation}
  \label{eq:atct:fb:sections}
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \dtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}
\end{equation}
such that each section function $\dsection: \dbasepoint \mapsto \delement$ maps from each point $\dbasepoint \in \openset$ to a corresponding record in the fiber space $\delement \in \dfiber_{\dbasepoint}$ over that point. Bundles can have multiple sections, as denoted by $\Gamma(\openset, \dtotal\restriction{\openset})$. We can therefore model data as structures that map from an index like point $\dbasepoint$ to a data record $\delement$, and encapsulate multiple datasets with the same fiber and base space as different sections of the same bundle.

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{fb_rho.pdf}
  \caption{The scatter marker is specified by the section $\gsection$, which maps into the fiber $\gfiber$ to retrieve the values that compose into the pixel (approximated as a square) returned by the section function evaluated at each point $\gbasepoint$. The section evaluated over the entire space $\gsection\vert_{S}$ returns the entire scatter mark, shown here in faded form to make it easier to see the individual pixels.
  \label{fig:atct:fb:graphic}}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[width=1\columnwidth]{tex/sheaf_rules.pdf}
  \caption{A sheaf has the conditions that sections are equal when they match on all subsets (\textit{locality}) and that the sections can be concatenated when they match on overlaps \textit{gluing}.\label{fig:atct:sheaf}}
\end{figure}

@@

\subsubsection{Example: Graphic and Data}
\begin{figure}[t]
  \includegraphics[width=1\textwidth]{xi_diagram.pdf}
  \caption{The data consists of the $sin$ and $cos$ functions over a unit circle base space. We choose to visualize this as a circle and two line plots. The indexing function \vindex\ book keeps \note{find better word than bookkeeping} which parts of the circle and each curve correspond to each point on the unit circle. The pushforward $\vindexpush$ matches each point in the data space to the specification of the graphic at that point, while the pullback $\vindexpull$ matches each point in the graphic space to the data over that point. \label{fig:atct:morphisms:sheaf}}
\end{figure}

@@

\begin{table}[H]
  \centering
  {\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|r | l l | }
    \hline
     & \textcolor{section}{section} & \textcolor{sheaf}{sheaf} \\
     & record at location & set of possible records for subset \\
     \hline
  Data & $ \cgamma{\dbasec}{\dtotalc} \ni \dsectionc: \dbase \textcolor{section}{\rightarrow} \dfiberc$ & $\sheafc_{\dbasec, \dtotalc}: \opensetc \rightarrow \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$\\
  Visual &  $\cgamma{\dbasec}{\vtotalc} \ni \vsectionc: \dbase \textcolor{section}{\rightarrow} \vfiberc$ & $\sheafc_{\dbasec, \vtotalc}: \opensetc \rightarrow \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}$\\
  Graphic &    $\cgamma{\gbasec}{\gtotalc} \ni \gsectionc: \gbase \textcolor{section}{\rightarrow} \gfiberc$ &  $\sheafc_{\gbasec, \gtotalc}: \opensetgc \rightarrow \cgamma{\opensetc}{\gtotalc\restriction_{\opensetgc}}$ \\
  \hline
  \end{tabular}
  \caption{Functions that associate topological subspaces with records, discussed in \autoref{sec:atct:fb:sections} and \autoref{sec:atct:sheaves}}
  \label{tab:appendix:summary:datafunctions}
  }
\end{table}

\begin{table}[H]
  {\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|r|l|}
    \hline
    merge & equation & behavior\\
    \hline
    indices  & $\dbasec_{a} \sqcup_{\dbasec_c} \dbasec_b$ & ${\dbasepoint \in \dbase_a, \dbase_b$ | $\dbasepoint_c \in \dbase_a, \dbase_b$ for all $dbase_ \in \dbasec$ \\
    \hline
    fields  & $\dfiberc_{a} \times_{\dfiberc_c} \dbase_c$
    \hline

  \caption{}
  \label{tab:appendix:summary:merge}
  }
\end{table}

\begin{table}[H]
  \centering
  {\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|r|l|}
    \hline
      axiom & applied to datasets and indexes \\
    \hline
     presheaf & given $\textcolor{base}{index_1} \subset \textcolor{base}{index_2}$:\\
        & $\exists\;\textcolor{section}{dataset}[\textcolor{base}{index_2}]$\\
      & $\Rightarrow \textcolor{section}{dataset}[\textcolor{base}{index_2}][\textcolor{base}{index_1}] = \textcolor{section}{dataset}[\textcolor{base}{index_1}]$\\
     &  $\exists\;\textcolor{section}{dataset}[\textcolor{base}{index_1}] \nRightarrow \exists\;\textcolor{section}{dataset}[\textcolor{base}{index_2}]$\\
     &\\
    \hline
    locality & $\textcolor{section}{dataset^1}[\textcolor{base}{i}] = \textcolor{section}{dataset^2}[\textcolor{base}{i}]\;\forall\; \textcolor{base}{i}\in \textcolor{base}{index}\;$ \\
     & $\Rightarrow \textcolor{section}{dataset^1}=\textcolor{section}{dataset^2}$ \\
    \hline
    gluing & $\textcolor{base}{i}=\textcolor{base}{j}$ and $\textcolor{section}{dataset^1}[\textcolor{base}{i}] = \textcolor{section}{dataset^2}[\textcolor{base}{j}]$ \\
     & $\textcolor{section}{dataset^3}\coloneq  \textcolor{section}{dataset^1}[\textcolor{base}{:i}]  \oplus \textcolor{section}{dataset^2}[\textcolor{base}{j:}]$ \\
\hline
  \end{tabular}
  \caption{Presheaf and sheaf constraints implemented by structure preserving data containers, discussed in \autoref{sec:atct:sheaves}}
  \label{tab:appendix:summary:sheaves}
  }
\end{table}

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{transition_maps.pdf}
  \caption{The cylinder is a trivial fiber bundle; therefore it can be decomposed into local trivalizations that only need identity
  maps to glue the trivializations together. The mobius band is a non-trivial bundle; therefore it can only be decomposed into trivializations where at least one transition map is not an identity map. }\label{fig:cyl_mob_bundles}
\end{figure}

@@

\section*{Acknowledgment}
\note{Acknowledge all the actual people}
The authors would like to thank the anonymous reviewers who gave constructive feedback on an earlier version of this paper. The authors are also grateful to  the various Matplotlib and Napari contributors, particularly Juan Nunez-Iglesias, and Nicolas Kruchten for their valuable feedback from the library developer perspective.
